\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,top=12mm,bottom=12mm,left=13mm,right=13mm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage[hidelinks]{hyperref}

\definecolor{ink}{HTML}{18212D}
\definecolor{muted}{HTML}{607080}
\definecolor{rule}{HTML}{C9D2DC}
\definecolor{accent}{HTML}{0B6F78}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\renewcommand{\familydefault}{\sfdefault}
\renewcommand\labelitemi{\textcolor{accent}{\raisebox{0.25ex}{\scriptsize$\bullet$}}}
\setlist[itemize]{leftmargin=12pt,itemsep=2.0pt,topsep=2.3pt,parsep=0pt,partopsep=0pt}

\newcommand{\sectiontitle}[1]{%
  \vspace{8.5pt}
  {\small\bfseries\color{accent}\MakeUppercase{#1}}\par
  \vspace{2.5pt}{\color{rule}\hrule height 0.55pt}\vspace{4.8pt}
}
\newcommand{\sideitem}[2]{%
  {\bfseries #1}\par{\small\color{muted}#2}\par\vspace{6pt}
}
\newcommand{\role}[3]{%
  {\bfseries #1}\hfill{\small\color{muted}#2}\par
  {\small\color{muted}#3}\par
}
\newcommand{\project}[3]{%
  {\bfseries #1}\hfill{\small\color{muted}#2}\par
  {\small #3}\par\vspace{4pt}
}

\begin{document}
\fontsize{10.0}{12.0}\selectfont
\color{ink}

{\LARGE\bfseries Alexander Belik}\hfill{\small Dublin, Ireland}\\[-1pt]
{\large\color{accent} Software Engineering \,|\, AI Systems \,|\, Scientific Computing}\hfill{\small +353 85 256 4027}\\[3pt]
{\small
\href{mailto:abelik1@outlook.com}{abelik1@outlook.com}
\quad|\quad
\href{https://www.linkedin.com/in/alexander-belik/}{linkedin.com/in/alexander-belik}
\quad|\quad
\href{https://github.com/ABelik1}{github.com/ABelik1}
}
\vspace{7pt}

{\color{rule}\hrule height 0.8pt}
\vspace{8pt}

\begin{minipage}[t][0.835\textheight][t]{0.315\linewidth}
\raggedright

\sectiontitle{Profile}
Theoretical Physics student and software builder focused on Python automation, AI systems, scientific ML, and practical full-stack tools.
\vspace{4pt}

I build software for messy real-world workflows: typed boundaries, reproducible data pipelines, inspectable automation, and interfaces people can actually use.

\sectiontitle{Core Stack}
{\small
Python, TypeScript, React\par
FastAPI, PyQt, SQLite\par
NumPy, SciPy, PyTorch\par
QuTiP, Optuna, Matplotlib\par
Selenium, Docker, Git\par
LaTeX, Markdown, Figma\par
}

\sectiontitle{Engineering Areas}
{\small
Backend APIs and services\par
Data scraping and normalization\par
Workflow automation\par
Local LLM orchestration\par
Tool routing and guarded actions\par
Scientific simulation\par
ML diagnostics and tuning\par
}

\sectiontitle{Education}
\sideitem{B.A. Theoretical Physics}{Trinity College Dublin, expected 2026}
{\small Focus: computational physics, quantum mechanics, statistical mechanics, and QFT.}\par\vspace{5pt}
\sideitem{Leaving Certificate}{The Dublin Academy of Education, 2020--2022}

\sectiontitle{Research Base}
{\small
Numerical simulation\par
Data analysis\par
Reservoir computing\par
Quantum dynamics\par
Experiment-control tooling\par
Technical writing\par
}

\vfill
\sectiontitle{Languages}
{\small English -- fluent\par Russian -- intermediate\par Spanish -- basic}

\end{minipage}
\hfill
\begin{minipage}[t][0.835\textheight][t]{0.645\linewidth}
\raggedright

\sectiontitle{Experience}

\role{Software Engineer, EdTech}{2024--2025}{Grinds360}
\begin{itemize}
  \item Built Python automation tools for video, content, and interactive lesson workflows.
  \item Contributed to full-stack product features and UX iteration with Figma-backed collaboration.
  \item Translated ambiguous product requirements into maintainable tools with non-technical stakeholders.
\end{itemize}
\vspace{2pt}

\role{Research Assistant, CRANN Institute}{Jun--Sep 2025}{Trinity College Dublin}
\begin{itemize}
  \item Built a PyTorch Echo State Network toolkit for quantum time-series prediction.
  \item Added configurable reservoirs, mixed precision, ridge-regression solvers, Optuna tuning, logging, and diagnostics.
  \item Validated predictions against Heisenberg spin-chain simulation data and conservation-law checks.
\end{itemize}
\vspace{2pt}

\role{Experimental / Computational Research Assistant}{May--Sep 2024}{Trinity College Dublin}
\begin{itemize}
  \item Created Python control and data-acquisition tooling for spectroscopy experiments on ferrofluids and liquid crystals.
  \item Improved repeatability through structured logging and automated measurement workflows.
\end{itemize}
\vspace{2pt}

\role{Teaching Assistant}{Oct 2025--Present}{Trinity College Dublin}
\begin{itemize}
  \item Lead weekly tutorials, support problem solving, and grade assignments with clear feedback.
\end{itemize}

\sectiontitle{Selected Projects}

\project{ORION / Big Brother Assistant}{Python, PyQt, Ollama, SQLite, Whisper}{Windows-first local assistant with wake-word gating, LLM-first capability selection, memory, guarded tools, daemon/direct/offline modes, and PyQt overlay/dashboard surfaces.}

\project{Choose Car}{React, TypeScript, FastAPI, SQLite, Selenium}{Ireland-focused keep-vs-switch car optimizer with backend services, admin review tools, OEM and used-inventory scraping, robots-aware indexed discovery, and normalization pipelines.}

\project{EchoState and Heisenberg Chain}{PyTorch, NumPy, SciPy, QuTiP, Optuna}{Reusable ESN library plus quantum spin-chain simulator for learning physical dynamics from observables, with solver comparisons and stability diagnostics.}

\project{DFT Hamilton / PySCF Environment}{Docker, Python, PySCF, LibXC}{Reproducible computational chemistry workflow for H2 RHF/DFT, open-shell Li UHF, molecular examples, spin-correlation tests, endpoint sensitivity checks, and custom functional comparisons.}

\vfill
\sectiontitle{Software Strengths}
{\small
\textbf{Practical architecture:} separates orchestration, persistence, UI, and side effects into testable boundaries.\\[2pt]
\textbf{Data-heavy workflows:} comfortable with scraping, raw/normalized databases, review surfaces, and repeatable imports.\\[2pt]
\textbf{Scientific reliability:} uses diagnostics, conservation checks, reproducible environments, and structured logs to make model behavior inspectable.
}

\end{minipage}

\end{document}
